\tool

### 2018-05-10 paper/paper.tex
Adding images to paper

Although software quality is important, software engineering tools created to improve code quality are often ignored by developers~\cite{Ivanov2017Gaps}. Tilley and colleagues suggest tool adoption should be one of the most important goals of software engineering research, and present challenges preventing professional developers from adopting programming tools created by researchers, or research-off-the-shelf (ROTS) software~\cite{Tilley2003ROTS}. Furthermore, researchers have explored barriers preventing software engineers from utilizing useful tools for debugging~\cite{Cao2010Debugging}, static analysis~\cite{Johnson2013Why}, security~\cite{Xiao2014Security}, refactoring~\cite{Murphy-HillBarriersRefactoring}, documentation~\cite{ForwardDocumentationRelevance}, and more. One barrier to tool adoption is the discoverability barrier, where users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}. This lack of tool awareness in the software engineering industry can lead to poor-quality applications, inconvenienced users, and wasted time and money fixing errors. Automated approaches have been developed to increase awareness of software tools and features, however Murphy-Hill and colleagues found that developers prefer learning about tools from colleagues during normal work activities, or \textit{peer interactions}~\cite{Murphy-Hill2011PeerInteraction}.

@@

The final step of our approach is to recommend useful software engineering tools to developers. The recommendation to developers includes commending them for improving code quality and apprehending new opportunities for similar improvements. In our example, the recommendation to the developer will praise them for their work refactoring the code, provide additional places in the code where they can make similar refactoring changes, and then suggest the refactoring tool which is useful for detecting even more instances for refactoring activities. Our goal is that through commending and apprehending, we can improve the effectiveness of recommendations for software engineering tools and increase adoption among developers.

%TODO: Non-lossy image
%TODO: More interesting error
\begin{figure*}
	\includegraphics[width=\textwidth]{images/screenshot.png}
	\caption{Screenshot of recommendation from \tool}	
	\label{fig:tool} 
\end{figure*}

@@

@@

This sections provides technical details on the implementation of our approach in \tool. The design of our system is motivated by current practices in the software engineering industry to make \tool~more similar to a peer for developers.

>>>>

Although software quality is important, software engineering tools created to improve code quality are often ignored by developers~\cite{Ivanov2017Gaps}. Tilley and colleagues suggest tool adoption should be one of the most important goals of software engineering research, and present challenges preventing professional developers from adopting programming tools created by researchers, or research-off-the-shelf (ROTS) software~\cite{Tilley2003ROTS}. Furthermore, researchers have explored barriers preventing software engineers from utilizing useful tools for debugging~\cite{Cao2010Debugging}, static analysis~\cite{Johnson2013Why}, security~\cite{Xiao2014Security}, refactoring~\cite{Murphy-HillBarriersRefactoring}, documentation~\cite{Forward2002Documentation}, and more. One barrier to tool adoption is the discoverability barrier, where users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}. This lack of tool awareness in the software engineering industry can lead to poor-quality applications, inconvenienced users, and wasted time and money fixing errors. Automated approaches have been developed to increase awareness of software tools and features, however Murphy-Hill and colleagues found that developers prefer learning about tools from colleagues during normal work activities, or \textit{peer interactions}~\cite{Murphy-Hill2011PeerInteraction}.

@@

The final step of our approach is to recommend useful software engineering tools to developers. The recommendation to developers includes commending them for improving code quality and apprehending new opportunities for similar improvements. In our example, the recommendation to the developer will praise them for their work refactoring the code, provide additional places in the code where they can make similar refactoring changes, and then suggest the refactoring tool which is useful for detecting even more instances for refactoring activities. Our goal is that through commending and apprehending, we can improve the effectiveness of recommendations for software engineering tools and increase adoption among developers. Figure \ref{fig:chartA} provides a general overview of how our approach can be implemented as an active help system.

%TODO: All non-lossy images
\begin{figure*}
	\includegraphics[width=\textwidth]{images/flowchartA.png}
	\caption{Flowchart presenting a general implementation of our approach}	
	\label{fig:chartA} 
\end{figure*}

@@

%TODO: More interesting error?
\begin{figure*}
	\includegraphics[width=\textwidth]{images/screenshot.png}
	\caption{Screenshot of recommendation from \tool}	
	\label{fig:tool} 
\end{figure*}

@@

This sections provides technical details on the implementation of our approach in \tool. Figure \ref{fig:chartB} shows a specific flowchart displaying the implementation of our design principles for the evaluation. The design of our system is motivated by current practices in the software engineering industry to make \tool~more similar to a peer for developers.

\begin{figure*}
	\includegraphics[width=\textwidth]{images/flowchartB.png}
	\caption{Flowchart presenting how we implemented our approach in \tool}	
	\label{fig:chartB} 
\end{figure*}
